This section consists description of the literature study performed during the development of this proposal.

\subsection{Fareclock}
Fareclock\cite{fareclock} is a web-based time clock software that offers features for employee time tracking, attendance management, and payroll processing. It provides businesses with tools to efficiently track employee work hours, monitor attendance, and generate accurate payroll reports. Fareclock allows employees to clock in and out using various methods such as biometric fingerprint scanning, web punch, mobile app, or phone call. The software also provides features like overtime tracking, PTO management, and shift scheduling. Fareclock aims to streamline the time management process and simplify payroll administration for businesses of all sizes.

\subsection{Learning Management System (Moodle)}

Moodle is a free and open-source learning management system. It has a variety of plugins to expand the features. There is a mod-attendance\cite{moodle_attendance} plugin also called Attendance Activity\cite{moodle_activity} where the instructor clicks on the "Update Attendance" button and is presented with a list of all the students in that course, along with configurable options and comments. The default options provided are Present, Absent, Late & Excused. Instructors can download the attendance for their course in Excel format or text format. Sessions can also be configured to allow students to record their own attendance and a range of different reports are available.

Presence offers several advantages over the mod-attendance plugin in Moodle, making it a more beneficial solution for automated attendance tracking in college classrooms.\\

Firstly, Presence provides a seamless and automated attendance tracking process, eliminating the need for manual input by instructors. Unlike the mod-attendance plugin, which requires instructors to manually update attendance by selecting options for each student, Presence utilizes sensors or other automated methods to track student entry into the classroom. This not only saves instructors significant time and effort but also ensures more accurate and reliable attendance data.\\

Secondly, Presence offers advanced data analysis and reporting capabilities. While the mod-attendance plugin in Moodle allows instructors to generate basic attendance reports, Presence takes data analysis to a higher level. It compiles and analyzes attendance data, providing valuable insights into attendance patterns, subject preferences, and even student behavior. This level of analysis can help instructors and administrators make informed decisions regarding teaching strategies, course planning, and student support, ultimately improving overall educational outcomes.\\

However, since Moodle is open-source we can use this technology and integrate it with Moodle.


\subsection{Existing Similar Appilcations}
While there may be similar plugins or programs available that offer alternative approaches to attendance tracking, "Presence" stands out by providing a comprehensive solution. It detects student arrivals, allowing for a more through analysis of attendance patterns. This valuable data can then be utilized to design improved timetables and curricula, ensuring optimal scheduling and enhancing the overall learning experience. By offering this unique functionality, Presence sets itself apart as a powerful tool for attendance management and curriculum optimization.

