The proposed deliverables for the Presence project align with the defined architecture and project objectives. These deliverables encompass various components and functionalities of the automated attendance system, ensuring a comprehensive solution for tracking and analyzing student attendance.\\

\textbf{Database Design and Implementation}\\
The first deliverable involves designing and implementing the database architecture that will serve as the backbone of the Presence system. This includes creating the necessary tables, relationships, and entities to store student information, attendance records, subject details, and other relevant data. The database design will prioritize efficiency, scalability, and data integrity.\\

\textbf{NodeJS Application}\\
The NodeJS application will form a crucial component of the Presence system. It will handle the communication between the database and the client application, enabling CRUD operations and WebSocket communication. The deliverable will include the development and deployment of the NodeJS application, ensuring its stability, security, and seamless integration with other system components.\\

\textbf{Client Application}\\
The client application will provide a user-friendly interface for students to access their attendance information securely. It will be designed with intuitive navigation, responsive design, and robust authentication mechanisms. The deliverable will include the development of the client application, ensuring compatibility across different devices and browsers.\\

\textbf{Authority Access and Reporting}\\
The Presence system will offer authorized personnel, such as administrators or instructors, access to comprehensive attendance data and reporting functionalities. This deliverable involves developing a secure login system for authorities, granting them access to view and analyze attendance records, generate reports, and gain insights into attendance patterns and subject preferences. The reporting component will leverage Python programs to generate insightful reports based on the collected data.