This section consists description of the literature study performed during the development of this proposal.

\subsection{Classroom Capture}
“Classroom Capture”\cite{reading_attendance} is primarily designed to record lectures and capture student attendance using cameras. The system is used by the University of California, San Diego to help students who miss classes due to illness or other reasons catch up on missed material. It also helps instructors monitor student attendance and engagement.

\subsection{Learning Management System (Moodle)}

Moodle is a free and open-source learning management system. It has a variety of plugins to expand the features. There is a mod-attendance\cite{moodle_attendance} plugin where the instructor clicks on the "Update Attendance" button and is presented with a list of all the students in that course, along with configurable options and comments. The default options provided are Present, Absent, Late & Excused. Instructors can download the attendance for their course in Excel format or text format. Sessions can also be configured to allow students to record their own attendance and a range of different reports are available.\\

Presence offers several advantages over the mod-attendance plugin in Moodle, making it a more beneficial solution for automated attendance tracking in college classrooms.\\

Firstly, Presence provides a seamless and automated attendance tracking process, eliminating the need for manual input by instructors. Unlike the mod-attendance plugin, which requires instructors to manually update attendance by selecting options for each student, Presence utilizes sensors or other automated methods to track student entry and exit from the classroom. This not only saves instructors significant time and effort but also ensures more accurate and reliable attendance data.\\

Secondly, Presence offers advanced data analysis and reporting capabilities. While the mod-attendance plugin in Moodle allows instructors to generate basic attendance reports, Presence takes data analysis to a higher level. It compiles and analyzes attendance data, providing valuable insights into attendance patterns, subject preferences, and even student behavior. This level of analysis can help instructors and administrators make informed decisions regarding teaching strategies, course planning, and student support, ultimately improving overall educational outcomes.\\

However, since Moodle is open-source we can use this technology and integrate it with Moodle.


\subsection{Existing Similar Appilcations}
While there may be similar plugins or programs available that offer alternative approaches to attendance tracking, "Presence" stands out by providing a comprehensive solution. It not only detects student arrivals but also tracks their departures, allowing for a more thorough analysis of attendance patterns. This valuable data can then be utilized to design improved timetables and curricula, ensuring optimal scheduling and enhancing the overall learning experience. By offering this unique functionality, Presence sets itself apart as a powerful tool for attendance management and curriculum optimization.

